### 2013-10-02 Paper_Markdown.Rmd
Commented out the individual site `cat` in the `j` loop for `bootstrap_mat`, added the pCCA ratio clump into `Paper_Markdown` methods to provide better choices of climate variables.  Began writing some results text for this section.  Finished July temp MAT bootstraps.

Model outputs
=========================
```{r LoadOutputs, echo=FALSE, message=FALSE, warning=FALSE}
load('data/wa.res.RData')
load('data/mat.res.RData')
load('data/wapls.res.RData')

>>>>

Climate Variables
=========================

We used the `r nrow(climate)` records from the North American Modern Pollen Database and associated climate data to provide reconstructions of key climatic variables. The process of calculating the lambda/lambda ratio from RDA (ref) produces interesting relationships, perhaps impacted by the breadth of the available climate and pollen data across North America.

```{r echo=FALSE, message=FALSE, warning=FALSE}
pol <- mod_pol[,7:ncol(mod_pol)]
clim <- climate[,4:ncol(climate)]

clim.ratio <- rep(NA, ncol(clim))

for(i in 1:ncol(clim)){
  test.struct <- rda(pol ~ clim[,i])
  clim.ratio[i] <- test.struct$CCA$tot.chi / test.struct$CA$tot.chi
}

names(clim.ratio) <- colnames(clim)

Key variables based on the $latex \frac {\lambda_1} {\lambda_2} $ using pCCA appear to be climate variables relating to mean monthly percent summer sunshine.  These variables are likely to be variables that are combinations of temperature and preciptiation variables, however this value is not linear, nor is it continuous, meaning that .  While Telford & Birks (2009) have criticised sunshine reconstructions (Freshette et al., 2008) in the past (and perhaps with good reason), the strength of the sunshine signal in the climate data is worth noting, but the limitations of CCA may impact our ability to detect and accurately assess its importance.

Model outputs
=========================

Once the climate variables of interest were established we began by bootstrapping the models for these climate variables.

```{r LoadOutputs, echo=FALSE, message=FALSE, warning=FALSE}
load('data/wa.res.RData')
load('data/mat.res.RData')
load('data/wapls.res.RData')
